Untitled

### 2024-02-05 MSR.rmd
Update

>>>>

## Inverse Transform Method

![](images/clipboard-3270173132.png){width="399"}

![](images/clipboard-2643393499.png){width="367"}

### Seragam

![](images/clipboard-1525824238.png){width="366"}

### Eksponensial

![](images/clipboard-2021265094.png){width="510"}

```{r}
i <- 1000
lambda <- 3 
U <- runif(i)
X <- -log(U)/lambda  
hist(X)
```

### Gamma

![](images/clipboard-1228991952.png){width="442"}

```{r}
#Gamma(α=5,β=3)  
i <- 1000
lambda <- 3 
alpha <- 5
U <- log(runif(i*alpha))  
Um <- matrix(U, i)
Y <- apply(Um, 1, sum) 
Gama <- -Y/lambda  
hist(Gama)
```

### Chi-Square

![](images/clipboard-3288057756.png){width="508"}

![](images/clipboard-4197710110.png){width="506"}

```{r}
#chi-square(10)  
i <- 1000
lambda <- 2 
alpha <- 5
U <- log(runif(i*alpha))  
Um <- matrix(U, i)
Y <- apply(Um, 1, sum) 
chi <- -Y/lambda  
hist(chi)

#chi-square(11)  
i <- 1000
lambda <- 2 
alpha < 5
U <- log(runif(i*alpha))  
Um <- matrix(U, i)
Y <- apply(Um, 1, sum) 
chi < --Y/lambda
chi <- chi +(rnorm(i))^2  
hist(chi)
```
